---
title: "Creating LaTeX syntax for Grattan's 'metrics tables'"
author: "Will Mackey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating LaTeX syntax for Grattan's 'metrics tables'}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First, install the `grattanMetricsTables` package:

```{r, eval = FALSE}
devtools::install_github("wfmackey/grattanMetricsTables")
```

Then load the `grattanMetricsTables` package and the `googlesheets4` package (to connect to the Google Sheets version of the metrics table).

```{r, eval = FALSE}
library(grattanMetricsTables)
library(googlesheets4)
```

The first of two steps is to read the Google Sheets metrics table. You'll have to guide `R` through this process the first time to give it access to the sheet:

```{r, eval = FALSE}
# Read and manipulate metrics data
# You will need to allow the googlesheets API access to your account
metrics <- read_sheet("1p2oz-9s29IN4M7paosSEG24A3GwVn3uskXP0-3npd4Q",
                      sheet = "Metric",
                      range = "A1:L42",
                      col_types = "c")
```

Once the sheet is loaded and assigned to an object, relay that object to the `make_metrics_table` function:

```{r, eval = FALSE}
# Generate the metrics tables:
make_metrics_tables(metrics) 
```

This will produce:

* A `metrics_table.tex` file that contains the 'innards' of the table (i.e. the metrics rows of the table) that can be copied-and-pasted into the table you have built.
* A folder `chapter_tables` with a `.tex` file for each chapter containing the full table environment.


# Reversing colour order
The function will look for the word 'higher' in the final column. If it is found, it will designate that column as a reversal instructions where:

"Higher number is..."
* "better": highest numbers will be yellow; lowest numbers will be red.
* "worse":  **reversed** lowest numbers will be yellow; highest numbers will be red.

